Augmenting the DonorsChoose.org Corpus for Meta-Learning \thanks{This publication emanated from research conducted with the financial support of Science Foundation Ireland (SFI) under Grant Number 13/RC/2106.}

### 2019-03-31 doc/paper/main.tex
paper/main.tex: Add graphics
Add visuals to the resource folder "doc/res". Furthermore, give the
files names which do not contain any special characters.

\begin{table}[ht]
	\centering
	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}%
	\label{tab:IllustrativeTable}
	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/Illustrative example of the overall design of the augmented transaction table}}}
\end{table}

@@

\begin{figure}[ht]
	\centering
	\subcaptionbox{Interactions Frequency\label{fig:InteractionFrequency}}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/DonorID - Distribution of number of interactions per user}}}
	}
	\hspace{2em}
	\subcaptionbox{Interaction Strength\label{fig:InteractionStrength}}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/DonationAmount - Distribution of ratings for logarithmic bins and excluded outliers}}}
	}
	\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}\label{fig:Interactions}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Learning subsystem - Position in Top-N test set}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the mean, the straight orange lines the median. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}%
	\label{fig:MetaLearnerStatistics}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/Meta-learner Performance - Average position in Top-N test set for various meta-learner algorithms with augmented learning subsystem filtering techniques}}}
	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
	\label{fig:MetaLearnerPerformance}
\end{figure}

>>>>

\begin{table}[ht]
	\centering
	\caption{Illustrative example of the overall design of the augmented transaction table with amended learning subsystem performance scores, statistics and meta-learner information.}%
	\label{tab:IllustrativeTable}
	\includegraphics[width=\textwidth,height=0.5\textheight,keepaspectratio]{{{../res/table}}}
\end{table}

@@

\begin{figure}[ht]
	\centering
	\subcaptionbox{Interactions Frequency\label{fig:InteractionFrequency}}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/number_interactions}}}
	}
	\hspace{2em}
	\subcaptionbox{Interaction Strength\label{fig:InteractionStrength}}{
		\includegraphics[width=0.45\textwidth,height=\textheight,keepaspectratio]{{{../res/distribtion_ratings}}}
	}
	\caption{The frequency of the number of interactions per user without outliers is shown in~\subref{fig:InteractionFrequency} and the distribution of the transformed interaction strength is shown in~\subref{fig:InteractionStrength}.}\label{fig:Interactions}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/learning_subsystem_position}}}
	\caption{Statistical features of the distributions of the recall-positions of the learning subsystem. The dashed green lines indicate the mean, the straight orange lines the median. The percentage below each algorithm indicates how often it is the best possible algorithm. To resolve a draw deterministically, the ``best'' algorithm is decided in alphabetic order.}%
	\label{fig:MetaLearnerStatistics}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=\textwidth,height=0.3\textheight,keepaspectratio]{{{../res/meta_learner_performance_average_position}}}
	\caption{Performance of the meta-learner system addressing the ASP. The dashed orange line represents the overall best algorithm, i.e., TF-IDF.}%
	\label{fig:MetaLearnerPerformance}
\end{figure}
